Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-12-04 contents/draft.tex
Response reviewer's comments: 1. Table 3 shows that syllable-based system shows better performance in written and spoken. It shows way better performance than dictionary-based(written) even with written data set. Is there any specific reason why the syllable-based shows better performance? It might be better to describe some insights for this. 2. Table 4 shows that Dictionary-based rerank shows better performance in all cases. However, the syllable-based shows a competitive performance in UC+EC (written and spoken). Can you explain or conjecture why that happened? 3. Page 9: 5th line from the

@@

    \begin{table*}[ht]
        \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}
        \label{tab:performance-with-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                       & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UC+EC (written)}                       & \multicolumn{2}{c}{UC+EC (spoken)}                        \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                             & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                          & 89.17                      & 93.06                        & 87.83                      & 92.19                        & 84.62                      & 89.60                        \\
            \hspace{2mm}Syllable-based                    & 91.95                      & 95.16                        & 97.42                      & 98.39                        & 95.53                      & \textbf{97.08}               \\
            \hspace{2mm}Dictionary-based (without rerank) & 95.23                      & 97.08                        & 96.59                      & 97.94                        & 93.49                      & 95.73                        \\
            \hspace{2mm}Dictionary-based (1-stage rerank) & 96.63                      & 97.84                        & 97.50                      & 98.44                        & 94.77                      & 96.62                        \\
            \hspace{2mm}Dictionary-based (2-stage rerank) & \textbf{96.87}             & \textbf{98.01}               & \textbf{97.75}             & \textbf{98.60}               & \textbf{95.56}             & \textbf{97.08}               \\
            \bottomrule
        \end{tabular*}
    \end{table*}

@@

    Initially, we conducted a comparison between the results of the dictionary-based morphological analysis model trained using the method outlined in Section~\ref{sec:morphological-analysis-model} and those of MeCab and syllable-based morphological analysis systems (refer to Table~\ref{tab:performance-without-reranking}).
    The outcomes indicate that the implemented dictionary-based method outperforms the existing MeCab system.
    However, it deviates from human evaluations due to the aforementioned limitations and does not attain the performance level of existing syllable-based morphological analysis systems.
    Additionally, we observed poor compatibility between the Sejong corpus and other corpora.
    The model trained on the Sejong corpus exhibits guaranteed performance when evaluated on the Sejong corpus, but some performance degradation occurs on other corpora.

@@

    Table~\ref{tab:performance-with-reranking} demonstrates that incorporating the re-ranking model significantly improves performance compared to no re-ranking.
    The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking.
    The second round of re-ranking further improves the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
    These performance improvements underscore the superiority of the dictionary-based morphological analysis model over traditional syllable-based morphological analysis systems, including those with numerous pre- and post-processing rules and dictionaries.

>>>>

    In our analysis, along with conventional metrics like eojeol accuracy and morpheme F1 score, we have introduced the Error Reduction Rate (ERR) as an additional metric to quantify performance improvements.
    The ERR is especially useful in contexts where differences in raw accuracy between models are minimal.
    This metric provides a more detailed understanding of the improvements by focusing on the reduction in the proportion of errors.
    This is particularly pertinent when comparing our dictionary-based model to the syllable-based system, which is already highly tuned.
    The Error Reduction Rate (ERR) is calculated using the following formula:
    \vspace{1mm}
    \[
        \footnotesize
        \text{ERR} = \left( \frac{\text{Error Rate}_{\text{baseline}} - \text{Error Rate}_{\text{improved}}}{\text{Error Rate}_{\text{baseline}}} \right) \times 100\%
    \]
    \vspace{0.5mm}

    In this context, the error rate is defined as \(1.0 - \text{Eojeol Accuracy}\), allowing us to focus specifically on the inaccuracies in eojeol recognition.

    By incorporating ERR into our evaluation, we aim to provide a more nuanced understanding of the improvements made by our proposed method.
    In some cases, the raw accuracy figures may be close, making it challenging to discern the significance of improvements.
    ERR helps to highlight the relative improvement in terms of error reduction, offering a clearer comparison between the models and underscoring the advancements of our approach, even in the context of marginal gains in accuracy.

@@

    \begin{table*}[ht]
        \caption{Performance comparison between morphological analysis systems with two-stage re-ranking}
        \label{tab:performance-with-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System}                       & \multicolumn{2}{c}{Sejong}                                             & \multicolumn{2}{c}{UC+EC (written)}                                    & \multicolumn{2}{c}{UC+EC (spoken)}                                     \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            ~                                             & \multicolumn{1}{c}{eojeol}              & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol}              & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol}              & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                          & 89.17                                   & 93.06                        & 87.83                                   & 92.19                        & 84.62                                   & 89.60                        \\
            \hspace{2mm}Syllable-based                    & 91.95                                   & 95.16                        & 97.42                                   & 98.39                        & 95.53                                   & \textbf{97.08}               \\
            \hspace{2mm}Dictionary-based (without rerank) & 95.23\footnotesize{ [+0.0\%]}           & 97.08                        & 96.59\footnotesize{ [+0.0\%]}           & 97.94                        & 93.49\footnotesize{ [+0.0\%]}           & 95.73                        \\
            \hspace{2mm}Dictionary-based (1-stage rerank) & 96.63\footnotesize{ [+29.2\%]}          & 97.84                        & 97.50\footnotesize{ [+26.7\%]}          & 98.44                        & 94.77\footnotesize{ [+19.6\%]}          & 96.62                        \\
            \hspace{2mm}Dictionary-based (2-stage rerank) & \textbf{96.87}\footnotesize{ [+34.4\%]} & \textbf{98.01}               & \textbf{97.75}\footnotesize{ [+34.1\%]} & \textbf{98.60}               & \textbf{95.56}\footnotesize{ [+31.8\%]} & \textbf{97.08}               \\
            \bottomrule
        \end{tabular*}
        \begin{tablenotes}
            \footnotesize
            \item\hspace{2mm} * The numbers in parentheses represent the Error Reduction Rate (ERR), calculated with respect to the ``Dictionary-based (without rerank)'' as the baseline.
        \end{tablenotes}
    \end{table*}

@@

    In our preliminary analysis, we compared the outcomes of our newly developed dictionary-based morphological analysis model, as detailed in Section~\ref{sec:morphological-analysis-model}, against the existing MeCab system and the syllable-based morphological analysis system.
    The findings, presented in Table~\ref{tab:performance-without-reranking}, demonstrate that our dictionary-based model surpasses the MeCab system in terms of accuracy.
    This indicates the effectiveness of our approach, which relies solely on a corpus-driven methodology without external dependencies like dictionaries or rule sets.

    However, when it comes to the syllable-based system, our model did not achieve comparable performance.
    The syllable-based system, as outlined in the research by Lee et al.~\cite{LeeCH2016}, has been substantially enhanced through the use of a pre-analyzed dictionary.
    This integration has significantly elevated its performance, allowing for more accurate handling of various linguistic elements.
    The system's ability to excel in different evaluation sets can be attributed to this comprehensive approach that combines extensive training corpora with meticulously crafted dictionaries and rules.

    Contrastingly, our dictionary-based system, being a recent innovation, does not utilize external resources such as pre-defined dictionaries or sets of linguistic rules.
    While this approach offers benefits like simplicity and potential adaptability, it also presents limitations in capturing the complexities and nuances of natural language that are efficiently managed by the syllable-based system.

    Additionally, our model exhibited compatibility issues between different corpora.
    The model trained on the Sejong corpus performed well when evaluated on the same corpus, but it showed a decline in performance when applied to other datasets.
    This points to the need for a more diverse and comprehensive training dataset to improve the model's generalizability.

    In summary, while our dictionary-based model marks an advancement in morphological analysis, the superior performance of the syllable-based system, especially as demonstrated in the study by Lee et al.~\cite{LeeCH2016}, highlights the effectiveness of combining training corpora with additional linguistic resources.
    Future enhancements to our model could involve integrating aspects of the syllable-based approach, such as incorporating rule-based methods or additional dictionaries, to further refine its performance.

@@

    Table~\ref{tab:performance-with-reranking} demonstrates that incorporating the re-ranking model significantly improves performance compared to no re-ranking.
    The error reduction rate (ERR) of the performance change from the existing dictionary-based model on eojeol accuracy is 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking.
    The second round of re-ranking further improves the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
    These performance improvements underscore the superiority of the dictionary-based morphological analysis model over traditional syllable-based morphological analysis systems, including those with numerous pre- and post-processing rules and dictionaries.
